method

### 2022-06-08 06_Paper/ER-ED/method.Rmd
added explanation on free text field
knitted document

The online survey will contain a number of questionnaires. 
In the focus of the current project is the Flexible Emotion Regulation Scale (FlexER)[@Doerfel2019].  
It assess flexible use of ER strategies with items such as "If I want to feel less negative emotions, I have several strategies to achieve this.", which we define as ER flexibility. 
The items are rated on a 4-point scale ranging from "strongly agree" to "strongly disagree".

@@

*Part three: ER choice.* <br> After the discounting part, participants will choose which one of the three ER strategies (distraction, distancing or suppression) they want to re-apply.
Importantly, there will be no further instruction on what basis they should make their decision.
Participants should make their decision freely, according to criteria they consider important for themselves.
However, participants will be asked to state the reasons for the decision afterwards.
As soon as they have decided, they will see the respective instruction and the block with another 20 negative pictures starts.

>>>>

The online survey will contain a number of questionnaires. 
In the focus of the current project is the Flexible Emotion Regulation Scale (FlexER)[@Doerfel2019].  
It assesses flexible use of ER strategies with items such as "If I want to feel less negative emotions, I have several strategies to achieve this.", which we define as ER flexibility. 
The items are rated on a 4-point scale ranging from "strongly agree" to "strongly disagree".

@@

*Part three: ER choice.* <br> After the discounting part, participants will choose which one of the three ER strategies (distraction, distancing or suppression) they want to re-apply.
Importantly, there will be no further instruction on what basis they should make their decision.
Participants should make their decision freely, according to criteria they consider important for themselves.
However, participants will be asked to state the reasons for the decision afterwards in RedCap using a free text field.
As soon as they have decided, they will see the respective instruction and the block with another 20 negative pictures starts.
